Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2018-04-03 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex Updated according to Andy's suggestion...

Now let us consider relaxing $\mathscr{I}$
to a countable set of finite-width intervals.
As the intervals in the image of a QIVPM become less and less sharp,
we expect more and more states to be consistent with it. In
the limit of minimal sharpness, all states~$\rho$
are consistent with the following QIVPM
\begin{equation}
\bar{\mu}\left(P\right)=\begin{cases}
\imposs & \textrm{ if }P=\mathbb{0}\\
\necess & \textrm{ if }P=\mathbb{1}\\
\unknown=\left[0,1\right] & \textrm{ otherwise}
\end{cases}
\end{equation}
mapping nearly all
projections to the \emph{unknown} interval. There is however a
subtlety: as shown in
the theorem below, it is possible for an arbitrary assignment of intervals to projectors
to be globally inconsistent.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgments}

\begin{acknowledgments}
The authors would like to thank the anonymous reviewers for their helpful and
constructive comments that greatly contributed to improving the final version of the paper.
\end{acknowledgments}

>>>>

Now let us consider relaxing $\mathscr{I}$
to a countable set of finite-width intervals.
As the intervals in the image of a QIVPM become less and less sharp,
we expect more and more states to be consistent with it. In
the limit of minimal sharpness, all states~$\rho$
are consistent with the following QIVPM
\begin{equation}
\bar{\mu}\left(P\right)=\begin{cases}
\imposs & \textrm{ if }P=\mathbb{0}\\
\necess & \textrm{ if }P=\mathbb{1}\\
\unknown=\left[0,1\right] & \textrm{ otherwise}
\end{cases}
\end{equation}%
mapping nearly all
projections to the \emph{unknown} interval. There is however a
subtlety: as shown in
the theorem below, it is possible for an arbitrary assignment of intervals to projectors
to be globally inconsistent.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{ACKNOWLEDGMENTS}

\begin{acknowledgments}
We gratefully acknowledge helpful comments from the anonymous reviewer that
greatly contributed to improving the final version of the paper.
\end{acknowledgments}
